models with mice

### 2024-03-25 withmice.Rmd
conducted cronbach's alpha test for coal eco-pol with mice

#print.psych(ecopolfit2, sort= TRUE, cut= 0.4)

@@

@@

ecopols_2fa <- '
  Ndevelop =~ DEVSOLAR + PRIDESOLAR + NPRIDESOLAR + PROSPERSOLAR + JOBSSOLAR 
  Pdevelop =~ HEALTHSOLAR + BEAUTYSOLAR + DISPLACESOLAR + POLLUTESOLAR + ENVOVERDEV
'

secopol_cfa <- cfa(ecopols_2fa, data = miecopols$cov_combined, std.lv = TRUE)
#summary(secopol_cfa, fit.measure= TRUE, standardized = TRUE)

@@

# Extract parameter estimates
sparams <- parameterEstimates(secopol_cfa, standardized = TRUE)%>%
   slice(1:(n()-13))

sparams1 <- sparams %>%
  mutate(rhs = case_when(
  rhs == "DISPLACESOLAR" ~ "Solar energy is leading to displacement of people from their land",
  rhs == "BEAUTYSOLAR" ~ "Solar energy spoils the natural beauty of the landscape",
  rhs == "POLLUTESOLAR" ~ "Solar energy increases pollution of air/water/land",
  rhs == "HEALTHSOLAR" ~ "Solar energy poses a great risk to the health of people living around it",
  rhs == "JOBSSOLAR" ~ "Solar energy will bring jobs to the local community",
  rhs == "PRIDESOLAR" ~ "I would be proud if my community used Solar energy",
  rhs == "NPRIDESOLAR" ~ "Solar energy is a mark of pride for our nation",
  rhs == "DEVSOLAR" ~ "Solar energy pushes forward the country's development",
  rhs == "PROSPERSOLAR" ~ "Solar energy brings economic prosperity to the surrounding regions",
  rhs == "RELYSOLAR" ~ "I don't like the idea that I have to rely on the government for electricity from Solar energy",
  rhs == "INDUSTRYSMALL" ~ "Large corporations are destroying the local industries in India and benefiting only a handful of people",
  rhs == "OWNERREG" ~ "Regardless of ownership, the government should pass strong regulations and implement them",
  rhs == "MECHANISATION" ~ "Rapid mechanization of work is taking away jobs from workers in this country",
  rhs == "ENVOVERDEV" ~ "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
    TRUE ~ as.character(rhs)
  )) %>%
  dplyr::select(!c(lhs,op, std.nox)) %>%
    rename(
    "Items" = rhs,
    "Loadings" = est,
    "Standard Error" = se,
    "zvalue" = z) %>%
  mutate(across(c("Loadings", "Standard Error", "zvalue"), round, 3))

sparams1$Scale <- NA
sparams1$Scale[1:5] <- "People Centered Development"
sparams1$Scale[6:10] <- "Nationalist Development"
sparams1 <- sparams1[, c("Scale", setdiff(names(sparams1), "Scale"))]

@@

@@

#print.psych(ecopolfitc, sort= TRUE, cut= 0.4)

@@

#print.psych(ecopolfitc2, sort= TRUE, cut= 0.4)

@@

ecopolc_2fa <- '
  Ndevelop =~ PRIDECOAL + NPRIDECOAL + DEVOVERENV +  DECISIONCEN + OWNERPVT + DECISIONCEN  + OWNERNOREG + DEVCOAL +PROSPERCOAL
  Pdevelop =~ BEAUTYCOAL + POLLUTECOAL + HEALTHCOAL + OWNERPUB + ENVOVERDEV + DISPLACECOAL

@@

cecopol_cfa <- cfa(ecopolc_2fa, data = miecopolc$cov_combined, std.lv = TRUE)
#summary(cecopol_cfa, fit.measure= TRUE, standardized = TRUE)

@@

\elandscape
### Alpha test

cNdevelop <-ecopolc %>%
  dplyr::select((c(PRIDECOAL, NPRIDECOAL, DEVOVERENV, DECISIONCEN, OWNERPVT, OWNERNOREG, ECONOMYGLOBAL, DEVCOAL, PROSPERCOAL)))

cNdevelop_alpha <- psych::alpha(cNdevelop, check.keys = TRUE) # alpha = 0.62

cPdevelop <-ecopolc %>%
  dplyr::select((c(BEAUTYCOAL , POLLUTECOAL , HEALTHCOAL , OWNERPUB , ENVOVERDEV , DISPLACECOAL)))

nPdevelop_alpha <- psych::alpha(nPdevelop , check.keys = TRUE) # alpha = 0.79

@@

>>>>

print.psych(ecopolfit2, sort= TRUE, cut=0.4)

@@

# covariance matrix fro mifa ecopol solar 
#miecopols$cov_combined

@@

ecopols_2fa <- '
  Ndevelop =~ DEVSOLAR + PRIDESOLAR + NPRIDESOLAR + PROSPERSOLAR + JOBSSOLAR
  Pdevelop =~ HEALTHSOLAR + BEAUTYSOLAR + DISPLACESOLAR + POLLUTESOLAR +ENVOVERDEV
'

secopol_cfa <- cfa(ecopols_2fa, sample.cov = miecopols$cov_combined, sample.nobs = 1099, std.lv = TRUE) # std.lv = TRUE to do variance standardization method
summary(secopol_cfa, fit.measure= TRUE, standardized = TRUE)

@@

# Extract parameter estimates
sparams <- parameterEstimates(secopol_cfa, standardized = TRUE)%>%
   slice(1:(n()-11))

sparams1 <- sparams %>%
  mutate(rhs = case_when(
  rhs == "DEVSOLAR" ~ "Solar energy pushes forward the country's development",
  rhs == "PRIDESOLAR" ~ "I would be proud if my community used Solar energy",
  rhs == "NPRIDESOLAR" ~ "Solar energy is a mark of pride for our nation",
  rhs == "PROSPERSOLAR" ~ "Solar energy brings economic prosperity to the surrounding regions",
  rhs == "JOBSSOLAR" ~ "Solar energy will bring jobs to the local community",
  rhs == "POLLUTESOLAR" ~ "Solar energy increases pollution of air/water/land",
  rhs == "HEALTHSOLAR" ~ "Solar energy poses a great risk to the health of people living around it",
  rhs == "BEAUTYSOLAR" ~ "Solar energy spoils the natural beauty of the landscape",
  rhs == "DISPLACESOLAR" ~ "Solar energy is leading to displacement of people from their land",
  rhs == "ENVOVERDEV" ~ "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
  rhs == "RELYSOLAR" ~ "I don't like the idea that I have to rely on the government for electricity from Solar energy",
  rhs == "INDUSTRYSMALL" ~ "Large corporations are destroying the local industries in India and benefiting only a handful of people",
  rhs == "OWNERREG" ~ "Regardless of ownership, the government should pass strong regulations and implement them",
  rhs == "MECHANISATION" ~ "Rapid mechanization of work is taking away jobs from workers in this country",
    TRUE ~ as.character(rhs)
  )) %>%
  dplyr::select(!c(lhs,op, std.nox)) %>%
    rename(
    "Items" = rhs,
    "Loadings" = est,
    "Standard Error" = se,
    "zvalue" = z) %>%
  mutate(across(c("Loadings", "Standard Error", "zvalue"), round, 3))

sparams1$Scale <- NA
sparams1$Scale[1:4] <- "People Centered Development"
sparams1$Scale[5:8] <- "Nationalist Development"
sparams1 <- sparams1[, c("Scale", setdiff(names(sparams1), "Scale"))]

@@

```{r fit-measures-display, echo = FALSE}
# Extract fit measures
fit_measuress <- fitMeasures(secopol_cfa, fit.measures = c("CFI", "TLI", "RMSEA", "rmsea.ci.upper", "rmsea.ci.lower"))
fit_measuress2 <- fitMeasures(secopol_cfa)
# Convert to a data frame for presentation
fit_dfs <- data.frame(Measure = names(fit_measuress), Value = fit_measuress) %>%
  mutate(Measure = case_when(
    Measure == "cfi" ~ "Comparative Fit Index (CFI) ",
    Measure == "tli" ~ "Tucker-Lewis Index (TLI)",
    Measure == "rmsea" ~ "Root Mean Square Error of Approximation(RMSEA)",
    Measure == "rmsea.ci.upper" ~ "RMSEA 90 Percent confidence interval - lower",
    Measure == "rmsea.ci.lower" ~ "RMSEA 90 Percent confidence interval - upper",
    TRUE ~ as.character(Measure)
  )) %>%
  mutate(Value = round(Value, 3)) %>%
  remove_rownames()

#RMSEA - between 0.05 and 0.08 (reasonable fit), less than 0.05 close fit and greater than 0.10 is poor fit 
#CFI - greater than 0.90 or 0.95 indicates good fit
#TFI - CFI>TFI >0.90 - indicates good fit

# Confirmatory Factor Analysis(CFA): Solar

```{r, echo =FALSE}
# Display fit measures using kable
knitr::kable(fit_dfs, caption = "Fit Measures: CFA Solar energy", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"))

@@

print.psych(ecopolfitc, sort= TRUE, cut= 0.4)

@@

print.psych(ecopolfitc2, sort= TRUE, cut= 0.4)

@@

ecopolc_2fa <- '
  Ndevelop =~ DEVCOAL+ PROSPERCOAL + NPRIDECOAL + PRIDECOAL  + JOBSCOAL + ECONOMYGLOBAL+ WEALTHLIM+ INDUSTRYLARGE+ DECISIONCEN + MECHANISATION + DEVOVERENV
  Pdevelop =~ BEAUTYCOAL + + HEALTHCOAL + POLLUTECOAL 
  Pdevelop2 =~  DISPLACECOAL  + ENVOVERDEV +OWNERPUB

@@

cecopol_cfa <- cfa(ecopolc_2fa, sample.cov = miecopolc$cov_combined, sample.nobs = 1099, std.lv = TRUE)
summary(cecopol_cfa, fit.measure= TRUE, standardized = TRUE)

@@

@@

### Alpha test

cNdevelop <-cecopol2 %>%
  dplyr::select((c(PRIDECOAL, NPRIDECOAL, DEVOVERENV, DECISIONCEN, OWNERPVT, OWNERNOREG, ECONOMYGLOBAL, DEVCOAL, PROSPERCOAL)))

cNdevelop_alpha <- psych::alpha(cNdevelop, check.keys = TRUE) # alpha = 0.75

cPdevelop <-cecopol2 %>%
  dplyr::select((c(BEAUTYCOAL , POLLUTECOAL , HEALTHCOAL , OWNERPUB , ENVOVERDEV , DISPLACECOAL)))

nPdevelop_alpha <- psych::alpha(nPdevelop , check.keys = TRUE) # alpha = 0.78
